%%Just type in text of your acknowledgments below.
%%Delete the text you don't like.

It's never easy going back to school, but it is especially difficult with a wife, three kids, and $17$ years removed from a formal classroom setting.  This adventure, and yes it has been an adventure, could not have been pursued without the love, support, and understanding of my wife, Julie.  Our children, Ethan, Isaac, and Audrey, have been tremendously patient while ``Daddy's on the laptop again!'', although there was the fair amount of ``When are you going to be finished with homework so that we can play a game?''.  I love you all very much and you may never understand how much you helped me through this.

I especially want to thank my adviser, Dr. Anderson, who was able to rekindle my passion for research and help me exercise those mathematical muscles that had atrophied many years prior.  Your guidance and advice on topics ranging from \LaTeX, to navigating the journal publication process, to linear algebra was greatly appreciated.  

I want to acknowledge and thank my graduate committee, Dr. Austen, Dr. Johnson, Dr. Radman, and Dr. Talbert, for their time and the guidance they provided throughout the dissertation process.  Dr. Johnson has been especially supportive in helping me navigate graduate school and, most importantly, in helping establish the cohort program that made this possible.

I want to sincerely thank Tennessee Tech University, the College of Engineering, and the Electrical and Computer Engineering Department, for patiently working with me and the other cohorts and for dedicating the resources to allow us to continue our advanced education. 

Last, but certainly not least, I could not have done this without my fellow cohorts, literally and figuratively.  Working together, we have been able to accomplish something great and I could not imagine going through this with another group of peers and friends.  You have all encouraged me tremendously and hopefully I have been able to give back a small measure of what I have received.

