% To compile vita alone, put a % symbol in front of "\comment" and "}%end of comment" below 
%    and take off the % symbol from "\end{document" at the bottom line. Undo before compiling
%    the complete thesis

\comment{
\documentclass[12pt]{report}   
\usepackage{ttuthesis}
    \report{Thesis}%default is Thesis, option Dissertation                         
\begin{document}
} %end of comment
\vitaname{VITA}
\vita

Jason Michael Vann was born and raised in Tennessee where he graduated with honors from Oliver Springs High School in $1993$.  After graduation, Michael entered the University of Tennessee, Knoxville with the assistance of the Herbert S. Walters' Scholarship and a National Merit Special Scholarship.   While an undergraduate he began his research path as an intern with the Monolithic Systems Development Group at Oak Ridge National Laboratory (ORNL).   After graduating \textit{summa cum laude} with a Bachelor of Science degree in electrical and computer engineering, he continued his research as a graduate student with the Joint University of Tennessee-ORNL program in mixed signal, very-large-scale-integration (VLSI) design.  After obtaining a Master of Science degree with a major in electrical engineering in August $1998$, he worked for the Department of Defense for several years before returning to ORNL in $2004$ as a research engineer.  He has served as director of ORNL's Signal Solutions Center and team lead for the Signals Exploitation Team where he coordinated the research and development efforts of a multi-disciplinary group focused on exploiting signals across multiple sensing modalities.  He entered the doctoral program at Tennessee Technological University in January $2015$ and in December $2017$ he was awarded his Ph.D. in electrical engineering.  He currently serves as a program manager within ORNL's Global Security Directorate.  His research interests are primarily focused on URE signal processing and the development of communication systems for disadvantaged environments.  

%\end{document}